Questions to Domain Experts

### 2020-05-13 StateOfPractice/Ao-Notes/Questions to Domain Experts.tex
Created a separate file for the questions to experts, and modified these questions

\title{Questions to Developers} 
\author{Ao Dong}
\date{\today}

@@

\section{Information about the developers and users}\citep{Jegatheesan2016}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item What is the typical background of a developer?
\item How large is the user group?
\item What is the typical background of a user?
\end{enumerate}

\section{Information about the software}

\ad{I drafted another version without considering our measurements}

\noindent\ad{3 aspects: dev process, software quality, user feedback}

\begin{enumerate}
\item Currently, what is the biggest obstacle against your development process?
\item In order to solve this problem, is there any improvement needed for your
development process?
\item In the past, is there any major obstacle to your development process that
has been solved? How did you solve it?
\item What is your project management process? Do you think improve this process
can tackle the current problem?
\item What is your documentation process? Do you think improve this process can
tackle the current problem?
\item Can you name several software qualities that are the most important to
this project?
\item Is any of them hard to be achieved? If yes, what methods have been considered
or practiced to improve the situation? If practiced, does it work?
\item Do you think the users can understand your software well? Has there been
any problem to use this software?
\item Do you think the current documentation can clearly convey all necessary
knowledge to the users? If yes, how did you successfully achieve it? If no, what
improvements are needed?
\end{enumerate}

\newpage

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}

>>>>

\title{Questions to Domain Experts} 
\author{Ao Dong}
\date{\today}

@@

\section{Paper}
\begin{itemize}
\item Where should we publish this paper?
\item Who are our targeted readers?
\end{itemize}

\section{Schedule \& Team}
\begin{itemize}
\item We propose to start this project from ... and finish it before ... . What
do you think?
\item Our meeting schedule is ... does it fit your plan?
\item We need ... extra members from your team, each working ... hours per week
for ... weeks. What do you think?
\item Is there any other experts you think we should keep them involved?
\end{itemize}

\section{Software List}
\begin{itemize}
\item The top 10 software of your choice?
\item What do you think of our process of selecting software candidates?
\item What do you think of the list of the selected software?
\item Is there any software you think should be removed from / added to the
list?
\end{itemize}

\section{Qualities \& Measurements}
\begin{itemize}
\item Are there any pain points when you develop/use software?
\item In order to test the usability, what is a good small task for the test?
\item Are there any suggestions on surface measure to qualities?
\item Are there any suggestions on deep measure to qualities?
\item Are there any suggestions on commonality analysis?
\end{itemize}

\section{Other}
\begin{itemize}
\item We are facing difficulties such as ..., do you have suggestions?
\item How to track our tasks. e.g. using GitHub issues.
\item Equipment such as computers, test tools, OS
\end{itemize}
